Detecting social information in a dense dataset of infants' natural visual experience

### 2020-01-30 paper/cogsci/paper.tex
updates to cogsci paper

\begin{abstract}
The faces and hands of infants' caregivers and other social partners
offer a rich source of social and causal information that may be
critical for infants' cognitive and linguistic development. Previous
work using manual annotation strategies and cross-sectional data has
found systematic changes in the proportion of faces and hands in the
egocentric perspective of young infants. Here, we examine the prevalence
of faces and hands in a longitudinal collection of over 1400 headcam
videos collected from three children along a span of 6 to 32 months of
age---the SAYcam dataset (Sullivan, Mei, Perfors, Wojcik, \& Frank,
under review). To analyze these naturalistic infant egocentric videos,
we first validate the use of a modern convolutional neural network for
pose detection (OpenPose) for the detection of faces and hands. We then
apply this model to the entire dataset, finding a decrease in the
proportion of faces vs.~hands across age up to the end of the second
year of life (Fausey, Jayaraman, \& Smith, 2016). In addition, we find
considerable variability in the proportion of faces/hands viewed by
children in different locations (e.g., living room vs.~kitchen),
demonstrating that variability across activity contexts may be a driving
factor in the amount of social information that infants' experience.

@@

Infants are confronted by a blooming, buzzing onslaught of stimuli
({\textbf{???}}) which they must learn to parse to make sense of the
world around them. Yet they do not embark on this learning process
alone: From as early as 3 months of age, young infants follow overt gaze
shifts (Gredeback, Fikke, \& Melinder, 2010), and even newborns prefer
to look at faces with direct vs.~averted gaze (Farroni, Csibra, Simion,
\& Johnson, 2002), despite their limited acuity. As faces are likely to
be an important conduit of social information that scaffolds cognitive
development, cognitive scientists have long hypothesized that faces are
prevalent in the visual experience of young infants.

Yet until recently most hypotheses about infants' visual experience have
gone untested. Though parents and scientists alike have strong
intuitions about what infant's see, even the viewpoint of a walking
child is not easily predicted by these intuitions (Clerkin, Hart, Rehg,
Yu, \& Smith, 2017; Franchak et al., 2011; Yoshida \& Smith, 2008). By
equipping infants and toddlers with head-mounted cameras, researchers
have begun to document the infant egocentric perspective on the world.
Using these methods, a growing body of work now demonstrates that the
viewpoints of very young infants (less than 4 months of age) are indeed
dominated by frequent, persistent views of the faces of their caregivers
(Jayaraman \& Smith, 2018; Jayaraman, Fausey, \& Smith, 2015; Sugden,
Mohamed-Ali, \& Moulson, n.d.).

As infants motor and cognitive abilities mature beyond these early
months, their perspective on the world becomes even more varied.
Crawlers see fewer faces and hands than do walking children
({\textbf{???}} papers; Sanchez, Long, Kraus, \& Frank, 2018) as well as
different view of objects ({\textbf{???}}). Further, as infants learn to
use their own hands to act on the world, they seem to focus on manual
actions taken by their social partners, as their perspective starts to
capture views of hands paired with the objects they are acting on
(Fausey et al., 2016). In turn, caregivers may start to use their hands
with more communicative intent, directing infants attention with
pointing and gestures to different events or objects during play
({\textbf{???}}).

Here, we analyze the social information present in the infant visual
perspective by analyzing a longitudinal collection of over 1400 headcam
videos collected from three children along a span of 6 to 32 months of
age---the SAYcam dataset (Sullivan et al., under review). In addition to
its size and longitudinal nature, this dataset is more naturalistic than
those previously used in two key ways. First, recordings were taken
under a large variety of contexts, encompassing infants' viewpoints
during both activities outside and inside the home. Even in other
naturalistic datasets, the incredible variety in a typical infant's
experience has been largely underrepresented (see examples in Figure 1;
e.g., riding in the car, gardening, watching chickens during a walk,
browsing magazines, nursing, brushing teeth). Second, the head-mounted
cameras used in the SAYcam dataset captured a substantially larger field
of view than those typically used, allowing a more complete picture of
the infant perspective. Head-mounted cameras with a more restricted
field of view do still capture where infants are foveating most of the
time ({\textbf{???}}, ({\textbf{???}})) but may still fail to capture
short saccades to either faces or hands in the periphery, as the
timescale of head movements is much longer.

With hundreds of hours of footage (\textgreater{}29M frames), this large
dataset necessitates a shift to an automated annotation strategy.
Indeed, annotation of the frames extracted from egocentric videos has
been prohibitively time-consuming, meaning that many frames are
typically not inspected, even in the most comprehensive studies. For
example, Fausey et al. (2016) collected a total of 143 hours of
head-mounted camera footage (15.5 million frames), of which one frame
every five seconds was hand annotated (by four coders), totalling
103,383 frames (per coder)---an impressive number of annotations but
nonetheless only 0.67\% of the collected footage. To address this
challenge, we use a modern computer vision model of pose detection to
automatically detect the presence of hands and faces from the infant
egocentric viewpoint. Specifically, we use OpenPose (Cao, Hidalgo,
Simon, Wei, \& Sheikh, 2018), a model optimized for jointly detecting
human face, body, hand, and foot keypoints that operates well on scenes
including multiple people, even if they are partially-occluded (see
Figure 1).

@@

As has been observed in other studies on automated annotation of headcam
data (e.g. {\textbf{???}}, ({\textbf{???}})), detection tasks that are
easy in third-person video can be quite challenging in egocentric
videos, due to difficult angles and sizes as well as substantial
occlusion. For example, the infant perspective often contains
non-canonical viewpoints of faces (e.g., looking up at a caregiver's
chin) as well as partially-occluded or oblique viewpoints of both faces
and hands.

@@

While these trends appear somewhat different than those observed in
Fausey et al. (2016), note that Fausey et al. (2016) included data from
very young infants (from 1-4 months of age), while here the youngest
videos coming from S and A around 6 and 9 months of age, respectively.
Similarly, our age range extends 8 months later than those infants in
Fausey et al. (2016), throughout a portion of third year of life.

@@

\caption[Proportion of faces vs]{Proportion of faces vs. hands in the entire dataset (A) and when hand detections are restricted to the upper 60 percent of the field of view (B). Data from each child (A, S) are plotted separately and binned by each week that the videos were filmed; data is scaled by the number of frames in that age range.}\label{fig:FaceVsHands}
\end{figure*}
\end{CodeChunk}

However, the most striking result is a much greater proportion of hands
in view than have previously been reported (Fausey et al., 2016). We
found this to be true across all ages, in both children, and regardless
of whether we analyzed human annotations (on the 24K random subset) or
OpenPose annotations on entire dataset. This is notable especially given
that OpenPose showed relatively low recall for hands, indicating that
this is still an underestimate of the proportion of hands in view. One
reason this could be the case is the much larger field of view that was
captured by the cameras used in this study: unlike previous studies, our
cameras were outfitted with a fish-eye lens in an attempt to capture as
much of the children's field of view as possible. Thus, the field of
view (FOV) of the fisheye lens used was larger (109 degrees horizontal x
70 degrees vertical) than the FOV of the lens used in many previous
studies; for example, in Fausey et al. (2016) the FOV was 69 x 41
degrees. This larger field of view may have allowed the SAYcam cameras
to capture not only the presence of a social partner's hands interacting
with objects, but also the children's own hands, leading to more
frequent hand detections.

@@

\caption[Density estimates for the child (left) and adult (right) hands that were detected int eh 24K random gold set]{Density estimates for the child (left) and adult (right) hands that were detected int eh 24K random gold set; each dot represents the center of a bounding box made by an adult participant.}\label{fig:density}
\end{figure}
\end{CodeChunk}

To assess this possibility, we obtained human annotations for a
subsample of 9051 frames in which a hand was detected in the random gold
set; participants (recruited via AMT) were asked to draw bounding boxes
around children's hands and adult's hands. Overall, we found that 34\%
of the hands in the random 24K sample were of children's own hands
(compared to 8\% reported in Fausey et al. (2016)) suggesting that this
difference in field of view did contribute substantially to the higher
rate of hand detections in the frames. Heatmaps of the bounding boxes
obtained from these annotations can be seen in Figure 3, showing that
children's hands tended to appear in the lower half of the frames.

We thus re-analyzed the entire dataset while restricting our analysis to
a smaller, upper portion of the frame comparable to the field of view
used in Fausey et al. (2016). To do so, we excluded hand detections that
occurred in the bottom 40\% of the frame, while retaining all hand
detections that occurred in the top 60\% of the frame. This coarse
cropping of decreased the proportion of hand detections from
0.3263743percent to 0.2156618 percent.

With this modified field of view, we now observed a more substantive
decrease across age in the proportions of faces relative to hands. To
quantify this trend, we fit a generalized linear mixed model to the
binned detection rates from this smaller field of field to estimate
changes in the proportion of faces vs.~hands over age. To better
approximate Fausey et al. (2016), we also restricted our analysis to the
age range seen in Fausey et al. (2016), excluding videos when children
were over 24 months of age, and indeed found that the proportion of
faces vs.~hands declined modestly with age (see Table 1).

@@

Broadly, the present analysis of this dense, longitudinal dataset has
yielded a better understanding of infants' evolving access to social
information. First, we found a relatively high proportion of faces in
view in the videos from the youngest age ranges in each child,
confirming previous findings (Fausey et al., 2016). This is particularly
notable given that, in cross-sectional data, this effect seems to be
most strongly driven by infants younger than 4 months of age (e.g.,
Fausey 2016; Jayaraman, Fausey, \& Smith, 2015; Sugden, Mohamed-Ali, \&
Moulson, 2014) who see both more frequent and more persistent faces
(Jayaraman \& Smith, 2018).

@@

Finally, we demonstrate the feasibility of using a modern, off-the-shelf
computer vision model to vastly increase the efficiency of processing
egocentric headcam footage, allowing us to annotate the entirety of very
large datasets (here, \textgreater{}30 million frames) for the presence
and size of people, hands, and faces, representing a 300-fold increase
in data relative to prior work (Fausey et al., 2016). As these
detections were imperfect compared to human annotators, fine-tuning
these models to better optimize for the infant viewpoint remains an open
avenue for future work. Standard computer vision models are rarely
exposed on these naturalistic, egocentric viewpoints, and we suspect
that training these models on more naturalistic data may lead to more
robust, generalizable detectors.

@@

\hypertarget{refs}{}
\hypertarget{ref-Cao2018openpose}{}
Cao, Z., Hidalgo, G., Simon, T., Wei, S.-E., \& Sheikh, Y. (2018).
OpenPose: Realtime multi-person 2D pose estimation using Part Affinity
Fields. In \emph{ArXiv preprint arXiv:1812.08008}.

@@

\hypertarget{ref-Gredeback2010}{}
Gredeback, G., Fikke, L., \& Melinder, A. (2010). The development of
joint visual attention: A longitudinal study of gaze following during
interactions with mothers and strangers. \emph{Developmental Science},
\emph{13}(6), 839--848.

@@

@@

@@

\hypertarget{ref-Sugden2014}{}
Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (n.d.). I spy with
my little eye: Typical, daily exposure to faces documented from a
first-person infant perspective. \emph{Developmental Psychobiology},
\emph{56}(2), 249--261.

@@

>>>>

\begin{abstract}
The faces and hands of infants' caregivers and other social partners
offer a rich source of social and causal information that may be
critical for infants' cognitive and linguistic development. Previous
work using manual annotation strategies and cross-sectional data has
found systematic changes in the proportion of faces and hands in the
egocentric perspective of young infants. Here, we examine the prevalence
of faces and hands in a longitudinal collection of over 1400 headcam
videos collected from three children along a span of 6 to 32 months of
age---the SAYcam dataset (Sullivan, Mei, Perfors, Wojcik, \& Frank,
under review). To analyze these naturalistic infant egocentric videos,
we first validate the use of a modern convolutional neural network for
pose detection (OpenPose) for the detection of faces and hands. We then
apply this model to the entire dataset, finding a decrease in the
proportion of faces vs.~hands across age up to the end of the second
year of life (C. M. Fausey, Jayaraman, \& Smith, 2016). In addition, we
find considerable variability in the proportion of faces/hands viewed by
children in different locations (e.g., living room vs.~kitchen),
demonstrating that variability across activity contexts may be a driving
factor in the amount of social information that infants' experience.

@@

Infants are confronted by a blooming, buzzing onslaught of stimuli
(James, Burkhardt, Bowers, \& Skrupskelis, 1890) which they must learn
to parse to make sense of the world around them. Yet they do not embark
on this learning process alone: From as early as 3 months of age, young
infants follow overt gaze shifts (Gredeb\wrapmf{\"{a}}ck, Theuring,
Hauf, \& Kenward, 2008), and even newborns prefer to look at faces with
direct vs.~averted gaze (Farroni, Csibra, Simion, \& Johnson, 2002),
despite their limited acuity. As faces are likely to be an important
conduit of social information that scaffolds cognitive development,
cognitive scientists have long hypothesized that faces are prevalent in
the visual experience of young infants.

Yet until recently most hypotheses about infants' visual experience have
gone untested. Though parents and scientists alike have strong
intuitions about what infant's see, even the viewpoint of a walking
child is not easily predicted by these intuitions (Clerkin, Hart, Rehg,
Yu, \& Smith, 2017; Franchak, Kretch, Soska, \& Adolph, 2011). By
equipping infants and toddlers with head-mounted cameras, researchers
have begun to document the infant egocentric perspective on the world.
Using these methods, a growing body of work now demonstrates that the
viewpoints of very young infants (less than 4 months of age) are indeed
dominated by frequent, persistent views of the faces of their caregivers
(Jayaraman \& Smith, 2018; Jayaraman, Fausey, \& Smith, 2015; Sugden,
Mohamed-Ali, \& Moulson, 2014).

As infants motor and cognitive abilities mature beyond these early
months, their perspective on the world becomes even more varied.
Crawlers see fewer faces and hands than do walking children (Franchak,
Kretch, \& Adolph, 2017; Kretch, Franchak, \& Adolph, 2014; A. Sanchez,
Long, Kraus, \& Frank, 2018) as well as different view of objects
(Smith, Yu, \& Pereira, 2011). Further, as infants learn to use their
own hands to act on the world, they seem to focus on manual actions
taken by their social partners, as their perspective starts to capture
views of hands paired with the objects they are acting on (C. M. Fausey
et al., 2016). In turn, caregivers may start to use their hands with
more communicative intent, directing infants attention with pointing and
gestures to different events or objects during play (Yu \& Smith, 2013).

Here, we analyze the social information present in the infant visual
perspective by analyzing a longitudinal collection of over 1400 headcam
videos collected from three children along a span of 6 to 32 months of
age---the SAYcam dataset (Sullivan et al., under review). In addition to
its size and longitudinal nature, this dataset is more naturalistic than
those previously used in two key ways. First, recordings were taken
under a large variety of contexts, encompassing infants' viewpoints
during both activities outside and inside the home. Even in other
naturalistic datasets, the incredible variety in a typical infant's
experience has been largely underrepresented (see examples in Figure 1;
e.g., riding in the car, gardening, watching chickens during a walk,
browsing magazines, nursing, brushing teeth). Second, the head-mounted
cameras used in the SAYcam dataset captured a substantially larger field
of view than those typically used, allowing a more complete picture of
the infant perspective. Head-mounted cameras with a more restricted
field of view do still capture where infants are foveating most of the
time (H. Yoshida \& Smith, 2008, Smith, Yu, Yoshida, \& Fausey (2015))
but may still fail to capture short saccades to either faces or hands in
the periphery, as the timescale of head movements is much longer.

With hundreds of hours of footage (\textgreater{}29M frames), this large
dataset necessitates a shift to an automated annotation strategy.
Indeed, annotation of the frames extracted from egocentric videos has
been prohibitively time-consuming, meaning that many frames are
typically not inspected, even in the most comprehensive studies. For
example, C. M. Fausey et al. (2016) collected a total of 143 hours of
head-mounted camera footage (15.5 million frames), of which one frame
every five seconds was hand annotated (by four coders), totalling
103,383 frames (per coder)---an impressive number of annotations but
nonetheless only 0.67\% of the collected footage. To address this
challenge, we use a modern computer vision model of pose detection to
automatically detect the presence of hands and faces from the infant
egocentric viewpoint. Specifically, we use OpenPose (Cao, Hidalgo,
Simon, Wei, \& Sheikh, 2018), a model optimized for jointly detecting
human face, body, hand, and foot keypoints that operates well on scenes
including multiple people, even if they are partially-occluded (see
Figure 1).

@@

As has been observed in other studies on automated annotation of headcam
data (e.g. M. C. Frank, Simmons, Yurovsky, \& Pusiol, 2013, Alessandro
Sanchez, Long, Kraus, \& Frank (2018), Bambach, Lee, Crandall, \& Yu
(2015)), detection tasks that are easy in third-person video can be
quite challenging in egocentric videos, due to difficult angles and
sizes as well as substantial occlusion. For example, the infant
perspective often contains non-canonical viewpoints of faces (e.g.,
looking up at a caregiver's chin) as well as partially-occluded or
oblique viewpoints of both faces and hands.

@@

While these trends appear somewhat different than those observed in C.
M. Fausey et al. (2016), note that C. M. Fausey et al. (2016) included
data from very young infants (from 1-4 months of age), while here the
youngest videos coming from S and A around 6 and 9 months of age,
respectively. Similarly, our age range extends 8 months later than those
infants in C. M. Fausey et al. (2016), throughout a portion of third
year of life.

@@

\caption[Proportion of faces (A), hands (B), and faces vs]{Proportion of faces (A), hands (B), and faces vs. hands (C) in the entire dataset and (D). when hand detections are restricted to the upper 60 percent of the field of view (B). Data from each child are plotted separately and binned by each week that the videos were filmed; data pointsscaled by the number of frames in that age range.}\label{fig:FaceVsHands}
\end{figure*}
\end{CodeChunk}

However, the most striking result is a much greater proportion of hands
in view than have previously been reported (C. M. Fausey et al., 2016).
We found this to be true across all ages, in both children, and
regardless of whether we analyzed human annotations (on the 24K random
subset) or OpenPose annotations on entire dataset. This is notable
especially given that OpenPose showed relatively low recall for hands,
indicating that this is still an underestimate of the proportion of
hands in view. One reason this could be the case is the much larger
field of view that was captured by the cameras used in this study:
unlike previous studies, our cameras were outfitted with a fish-eye lens
in an attempt to capture as much of the children's field of view as
possible. Thus, the field of view (FOV) of the fisheye lens used was
larger (109 degrees horizontal x 70 degrees vertical) than the FOV of
the lens used in many previous studies; for example, in C. M. Fausey et
al. (2016) the FOV was 69 x 41 degrees. This larger field of view may
have allowed the SAYcam cameras to capture not only the presence of a
social partner's hands interacting with objects, but also the children's
own hands, leading to more frequent hand detections.

@@

\caption[Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set]{Density estimates for the child (left) and adult (right) hands that were detected in teh 24K random gold set; each dot represents the center of a bounding box made by an adult participant.}\label{fig:density}
\end{figure}
\end{CodeChunk}

To assess this possibility, we obtained human annotations for a
subsample of 9051 frames in which a hand was detected in the random gold
set; participants (recruited via AMT) were asked to draw bounding boxes
around children's hands and adult's hands. Overall, we found that 34\%
of the hands in the random 24K sample were of children's own hands
(compared to 8\% reported in C. M. Fausey et al. (2016)) suggesting that
this difference in field of view did contribute substantially to the
higher rate of hand detections in the frames. Heatmaps of the bounding
boxes obtained from these annotations can be seen in Figure 3, showing
that children's hands tended to appear in the lower half of the frames.

We thus re-analyzed the entire dataset while restricting our analysis to
a smaller, upper portion of the frame comparable to the field of view
used in C. M. Fausey et al. (2016). To do so, we excluded hand
detections that occurred in the bottom 40\% of the frame, while
retaining all hand detections that occurred in the top 60\% of the
frame. This coarse cropping of decreased the proportion of hand
detections from 0.3263743percent to 0.2156618 percent.

With this modified field of view, we now observed a more substantive
decrease across age in the proportions of faces relative to hands. To
quantify this trend, we fit a generalized linear mixed model to the
binned detection rates from this smaller field of field to estimate
changes in the proportion of faces vs.~hands over age. To better
approximate C. M. Fausey et al. (2016), we also restricted our analysis
to the age range seen in C. M. Fausey et al. (2016), excluding videos
when children were over 24 months of age, and indeed found that the
proportion of faces vs.~hands declined modestly with age (see Table 1).

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\ 
  \hline
(Intercept) & -0.26 & 0.09 & -2.83 & 0.005 \\ 
  scale(age\_months) & -0.15 & 0.00 & -225.40 & 0.000 \\ 
   \hline
\end{tabular}
\caption{Model coefficients from a generalized linear mixed model predicting the proportion of faces vs. hands seen by infants.} 
\end{table}

@@

Broadly, the present analysis of this dense, longitudinal dataset has
yielded a better understanding of infants' evolving access to social
information. First, we found a relatively high proportion of faces in
view in the videos from the youngest age ranges in each child,
confirming previous findings (C. M. Fausey et al., 2016). This is
particularly notable given that, in cross-sectional data, this effect
seems to be most strongly driven by infants younger than 4 months of age
(e.g., Fausey 2016; Jayaraman, Fausey, \& Smith, 2015; Sugden,
Mohamed-Ali, \& Moulson, 2014) who see both more frequent and more
persistent faces (Jayaraman \& Smith, 2018).

@@

Finally, we demonstrate the feasibility of using a modern, off-the-shelf
computer vision model to vastly increase the efficiency of processing
egocentric headcam footage, allowing us to annotate the entirety of very
large datasets (here, \textgreater{}30 million frames) for the presence
and size of people, hands, and faces, representing a 300-fold increase
in data relative to prior work (C. M. Fausey et al., 2016). As these
detections were imperfect compared to human annotators, fine-tuning
these models to better optimize for the infant viewpoint remains an open
avenue for future work. Standard computer vision models are rarely
exposed on these naturalistic, egocentric viewpoints, and we suspect
that training these models on more naturalistic data may lead to more
robust, generalizable detectors.

@@

\hypertarget{refs}{}
\hypertarget{ref-bambach2015lending}{}
Bambach, S., Lee, S., Crandall, D. J., \& Yu, C. (2015). Lending a hand:
Detecting hands and recognizing activities in complex egocentric
interactions. In \emph{Proceedings of the ieee international conference
on computer vision} (pp. 1949--1957).

\hypertarget{ref-Cao2018openpose}{}
Cao, Z., Hidalgo, G., Simon, T., Wei, S.-E., \& Sheikh, Y. (2018).
OpenPose: Realtime multi-person 2D pose estimation using Part Affinity
Fields. In \emph{ArXiv preprint arXiv:1812.08008}.

\hypertarget{ref-clerkin2017}{}
Clerkin, E. M., Hart, E., Rehg, J. M., Yu, C., \& Smith, L. B. (2017).
Real-world visual statistics and infants' first-learned object names.
\emph{Phil. Trans. R. Soc. B}, \emph{372}(1711), 20160055.

@@

\hypertarget{ref-franchak2017see}{}
Franchak, J. M., Kretch, K. S., \& Adolph, K. E. (2017). See and be
seen: Infant--caregiver social looking during locomotor free play.
\emph{Developmental Science}.

\hypertarget{ref-franchak2011}{}
Franchak, J. M., Kretch, K. S., Soska, K. C., \& Adolph, K. E. (2011).
Head-mounted eye tracking: A new method to describe infant looking.
\emph{Child Development}, \emph{82}(6), 1738--1750.

\hypertarget{ref-frank2013}{}
Frank, M. C., Simmons, K., Yurovsky, D., \& Pusiol, G. (2013).
Developmental and postural changes in childrens visual access to faces.
In \emph{Proceedings of the 35th annual meeting of the cognitive science
society} (pp. 454--459).

\hypertarget{ref-gredeback2008microstructure}{}
Gredeb\wrapmf{\"{a}}ck, G., Theuring, C., Hauf, P., \& Kenward, B.
(2008). The microstructure of infants' gaze as they view adult shifts in
overt attention. \emph{Infancy}, \emph{13}(5), 533--543.

\hypertarget{ref-james1890principles}{}
James, W., Burkhardt, F., Bowers, F., \& Skrupskelis, I. K. (1890).
\emph{The principles of psychology} (Vol. 1). Macmillan London.

@@

\hypertarget{ref-kretch2014}{}
Kretch, K. S., Franchak, J. M., \& Adolph, K. E. (2014). Crawling and
walking infants see the world differently. \emph{Child Development},
\emph{85}(4), 1503--1518.

@@

\hypertarget{ref-sanchez2018postural}{}
Sanchez, A., Long, B., Kraus, A. M., \& Frank, M. C. (2018). Postural
developments modulate children's visual access to social information.

@@

\hypertarget{ref-smith2011not}{}
Smith, L. B., Yu, C., \& Pereira, A. F. (2011). Not your mother?s view:
The dynamics of toddler visual experience. \emph{Developmental Science},
\emph{14}(1), 9--17.

\hypertarget{ref-smith2015contributions}{}
Smith, L. B., Yu, C., Yoshida, H., \& Fausey, C. M. (2015).
Contributions of head-mounted cameras to studying the visual
environments of infants and young children. \emph{Journal of Cognition
and Development}, \emph{16}(3), 407--419.

\hypertarget{ref-Sugden2014}{}
Sugden, N. A., Mohamed-Ali, M. I., \& Moulson, M. C. (2014). I spy with
my little eye: Typical, daily exposure to faces documented from a
first-person infant perspective. \emph{Developmental Psychobiology},
\emph{56}(2), 249--261.

@@

\hypertarget{ref-yoshida2008}{}
Yoshida, H., \& Smith, L. (2008). What's in view for toddlers? Using a
head camera to study visual experience. \emph{Infancy}, \emph{13},
229--248.

\hypertarget{ref-yu2013joint}{}
Yu, C., \& Smith, L. B. (2013). Joint attention without gaze following:
Human infants and their parents coordinate visual attention to objects
through eye-hand coordination. \emph{PloS One}, \emph{8}(11).
